\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-07-04 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating Sec. V

\begin{remark}
We emphasize here that the network reduced model \eqref{ItoSDEcomponentlevel} is obtained from the so-called structure preserving power network model \cite{odun2012structure} after applying the Kron reduction \cite{dorfler2012kron}, and therefore, has all-to-all connection topology.	
\end{remark}

With the $i$-th generator, we associate its inertia $m_{i}>0$ and damping coefficient $\gamma_{i}>0$. The other parameters: the \emph{effective power input} $P_{i}$, the \emph{phase shift} $\varphi_{ij}\in[0,\frac{\pi}{2})$, and the \emph{coupling coefficients} $k_{ij}\geq 0$, depend on the network reduced admittance matrix $\bm{Y}\equiv[Y_{ij}]_{i,j=1}^{n}\in\mathbb{C}^{n\times n}$. Specifically,
\begin{subequations}
\begin{align}
 P_{i} &= P_{i}^{\text{mech}} - P_{i}^{\text{load}} - |V_{i}|^{2} \Re\left(Y_{ii}\right) + \Re\left(V_i \cdot I_{i}^{*}\right),\\
 \varphi_{ij} &= \begin{cases} -\arctan\left(\dfrac{\Re\left(Y_{ij}\right)}{\Im\left(Y_{ij}\right)}\right), & \text{if}\;i\neq j,\\
 0, & \text{otherwise},
 \end{cases}\\
 k_{ij} &= \begin{cases} |V_{i}| |V_{j}| \vert Y_{ij}\vert, & \text{if}\;i\neq j,\\
 0, & \text{otherwise},
 \end{cases}
\end{align}
\end{subequations}
where $P_{i}^{\text{mech}}$ is the mechanical power input, and $|V_{i}|$ is the voltage magnitude for generator $i$. {\red{{\textbf{Xinbo:}} One sentence saying any approximation made in (2) by using $V_{i}$ instead of the internal voltage $E_{i}$}}

>>>>

\begin{remark}
We emphasize here that the network-reduced model \eqref{ItoSDEcomponentlevel} is obtained from the so-called structure preserving power network model \cite{odun2012structure} after applying the Kron reduction \cite{dorfler2012kron}, and therefore, has all-to-all connection topology.	
\end{remark}

With the $i$th generator, we associate its inertia $m_{i}>0$ and damping coefficient $\gamma_{i}>0$. The other parameters: the \emph{effective power input} $P_{i}$, the \emph{phase shift} $\varphi_{ij}\in[0,\frac{\pi}{2})$, and the \emph{coupling coefficients} $k_{ij}\geq 0$, depend on the network reduced admittance matrix $\bm{Y}\equiv[Y_{ij}]_{i,j=1}^{n}\in\mathbb{C}^{n\times n}$. Specifically,
\begin{subequations}
\begin{align}
 P_{i} &= P_{i}^{\text{mech}} - P_{i}^{\text{load}} - |V_{i}|^{2} \Re\left(Y_{ii}\right) + \Re\left(V_i \cdot I_{i}^{*}\right),\\
 \varphi_{ij} &= \begin{cases} -\arctan\left(\dfrac{\Re\left(Y_{ij}\right)}{\Im\left(Y_{ij}\right)}\right), & \text{if}\;i\neq j,\\
 0, & \text{otherwise},
 \end{cases}\\
 k_{ij} &= \begin{cases} |V_{i}| |V_{j}| \vert Y_{ij}\vert, & \text{if}\;i\neq j,\\
 0, & \text{otherwise},
 \end{cases}
\end{align}
\end{subequations}
where $P_{i}^{\text{mech}}$ is the mechanical power input, $P_{i}^{\text{load}}$ is {\red{the real load (ignoring reactive load)}}, and $|V_{i}|$ is the voltage magnitude for generator $i$. {\red{{\textbf{Xinbo:}} One sentence saying any approximation made in (2) by using $V_{i}$ instead of the internal voltage $E_{i}$}}
